### 2020-05-01 serial.tex
minor tweaks

While we focused on the effect of epidemiological dynamics on the serial-interval distributions, other factors, such as intervention strategies, can also affect the generation- and serial-interval distributions.
Individual-level interventions, such as case isolation, directly affect individual's ability to transmit and will shorten the forward generation- and serial-intervals.
On the other hand, population-level interventions, such as social distancing, have qualitatively similar effects on epidemiogical dynamics as susceptible depletion;
therefore, we expect these intervention efforts to also shorten the forward generation- and serial-intervals.

Despite these limitations, our analysis of serial intervals of COVID-19 from China provide further support for our theoretical framework, demonstrating temporal variation in serial intervals and their effects on the estimates of \RR.
To our knowledge, most existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
Our study provides a rationale for reassessing estimates of serial-interval distributions, and their use in estimating \Ro, of the COVID-19 pandemic.

>>>>

While we focused on the effect of epidemiological dynamics on the serial-interval distributions, other factors, such as intervention strategies, can also affect the generation- and serial-interval distributions.
Individual-level interventions, such as case isolation, directly affect individual's ability to transmit and will shorten the forward generation- and serial-intervals.
Population-level interventions, such as social distancing, have qualitatively similar effects on epidemiogical dynamics as susceptible depletion;
therefore, we expect these intervention efforts to also (indirectly) shorten the forward generation- and serial-intervals.
\swp{Sunky suggested: ``Social distancing will squeeze the contacts into the household, thus introduce high degree of clustering, which will shorten the generation interval as well (running out of susceptible within the household before the infectious period ends).'' and I like the idea of mentioning this briefly and cite our previous contact\_trace paper... don't have a good sentence at the moment so I'm just going to leave it as is.}

Despite these limitations, our analysis of serial intervals of COVID-19 from China provide further support for our theoretical framework, demonstrating temporal variation in serial intervals and their effects on the estimates of \RR.
To our knowledge, most existing estimates of the serial-intervals of COVID-19 implicitly or explicitly assume that the serial-interval distributions remain constant throughout the course of an epidemic \citep{du2020serial, he2020temporal, nishiura2020serial,tindale2020transmission,zhao2020estimating,zhang2020evolving}.
Our study provides a rationale for reassessing estimates of serial-interval distributions, and their use in estimating \RR, of the COVID-19 pandemic.
